\section{Introduction}

As power dissipation becomes a major concern in a variety of computer systems, measuring power consumption becomes essential for hardware and software designs. 
However, it has been very difficult to obtain powers numbers accurately as well as quickly. 
RTL or gate-level simulation can provide reliable power numbers, but they are notoriously slow. 
Analytic methods can provide power numbers quickly and readily, but they are inaccurate and not adequate for detailed power analysis. 
Cycle accurate software power simulators such as Wattch~\cite{Wattch} and McPAT~\cite{McPat} have been favored by computer architects. 
However, they are not only time-consuming, but also less accurate.

In this project, we will propose FPGA-accelerated power simulators.  
This makes it possible to measure power consumption of the systems much more quickly and accurately. 
There are two major steps for fast power simulations, power model generation and counter structure generation. 
Fast power simulation starts from the Chisel designs which are converted into RTL by the Chisel verilog backend.
The power model generator approximates the design's power consumption using RTL signal activities.
It also reduce the signal list to be counted in FPGA simulation.
Then, counter structure generator adds the activity counters for the selected signals in the power model.
The design with the activity counters is ported to and simulated on FPGA.
With the power model, counter values from FPGA simulation provide the accurate and fast power analysis for the target design.